Pre-Trained Denoising Autoencoders Long Short-Term Memory Networks as probabilistic

### 2023-01-20 slides.Rmd
Fri Jan 20 13:00:09 CET 2023: update-remote.sh

---
title: "Pre-Trained Denoising Autoencoders Long Short-Term Memory Networks as probabilistic Models for Estimation of Distribution Genetic Programming"
subtitle: "Kolloquium zur Masterarbeit im M.Sc. Wirtschaftspädagogik "
author: "Roman Hoehn"
institute: "JGU Mainz"
date: "Datum: 25.01.2023"
#fontsize: 11pt
link-citations: true
output:
  beamer_presentation:
    theme: "Madrid"
    fonttheme: "structurebold"
    fig_width: 12
    fig_height: 10
    # keep_tex: true
    fig_caption: no
    number_sections: true
    slide_level: 2
toc: yes
bibliography: ref/ref.bib
csl: csl/harvard-cite-them-right.csl
lang: de
includes:
      in_header: [header_files/slides.tex]

---

@@

```{r, echo=FALSE, out.height="90%"}
knitr::include_graphics("./img/flowcharts/dae-gp.png")
```

@@

```{r, echo=FALSE, out.height="90%"}
knitr::include_graphics("./img/flowcharts/pt-dae-gp.png")
```

@@

```{r, echo=FALSE, out.height="90%"}
knitr::include_graphics("~/masterThesis/master_thesis/img/airfoil_2hl_maxIndSize_fullRun_30gens_withGP/median_fitness_byGens.png")
```

@@

```{r, echo=FALSE, out.height="90%"}
knitr::include_graphics("~/masterThesis/master_thesis/img/airfoil_2hl_maxIndSize_fullRun_30gens/final_fit_boxplot.png")
```

@@

```{r, echo=FALSE, out.height="90%"}
knitr::include_graphics("~/masterThesis/master_thesis/img/airfoil_2hl_maxIndSize_fullRun_30gens_withGP/median_best_Size_byGens.png")
```

@@

```{r, echo=FALSE, out.height="90%"}
knitr::include_graphics("/Users/rmn/github/master_thesis/img/airfoil_2hl_maxIndSize_fullRun_30gens_withGP/median_popDiversity_byGens_levOnly_withGP.png")
```

@@

```{r, echo=FALSE, out.height="90%"}
knitr::include_graphics("/Users/rmn/github/master_thesis/img/airfoil_2hl_maxIndSize_fullRun_30gens_TimeBenchmark/median_runtime.png")
```

@@

```{r, echo=FALSE, out.height="90%"}
knitr::include_graphics("/Users/rmn/github/master_thesis/img/airfoil_2hl_maxIndSize_fullRun_30gens_TimeBenchmark/median_training_epochs.png")
```

@@

```{r, echo=FALSE, out.height="90%"}
knitr::include_graphics("/Users/rmn/github/master_thesis/img/airfoil_2hl_maxIndSize_fullRun_30gens_TimeBenchmark/median_sampleTime.png")
```

@@

```{r, echo=FALSE, out.height="90%"}
knitr::include_graphics("/Users/rmn/github/master_thesis/img/Airfoil_RuntimeProfiling/Runtime_Bar.png")
```

@@

```{r, echo=FALSE, out.height="90%"}
knitr::include_graphics("~/masterThesis/master_thesis/img/airfoil_1hl_maxIndSize_fullRun_30gens/median_fitness_byGens.png")
```

@@

```{r, echo=FALSE, out.height="90%"}
knitr::include_graphics("~/masterThesis/master_thesis/img/airfoil_1hl_maxIndSize_fullRun_30gens/final_fit_boxplot.png")
```

@@

```{r, echo=FALSE, out.height="90%"}
knitr::include_graphics("~/masterThesis/master_thesis/img/airfoil_1hl_maxIndSize_fullRun_30gens/median_Size_byGens.png")
```

@@

```{r, echo=FALSE, out.height="90%"}
knitr::include_graphics("~/masterThesis/master_thesis/img/symbolicRegressionSummarized/median_fitness_byGens.png")
```
<!-- ![Übersicht Median Fitness - Symbolische Regression](~/masterThesis/master_thesis/img/symbolicRegressionSummarized/median_fitness_byGens.png){height=80%} -->

@@

```{r full_run_realWorldSymReg_fitness, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
library(knitr)
library(kableExtra)
library(dplyr)

@@

```{r, echo=FALSE, out.height="90%"}
knitr::include_graphics("~/masterThesis/master_thesis/img/symbolicRegressionSummarized/median_bestSol_size_byGens.png")
```

@@

```{r, echo=FALSE, out.height="90%"}
knitr::include_graphics("~/masterThesis/master_thesis/img/symbolicRegressionSummarized/median_levDistance_byGen.png")
```

@@

```{r, echo=FALSE, out.height="90%"}
knitr::include_graphics("~/masterThesis/master_thesis/img/symbolicRegressionSummarized/median_epochsTrained.png")
```

@@

```{r, echo=FALSE, out.height="90%"}
knitr::include_graphics("~/masterThesis/master_thesis/img/PT_Strategies_airfoil_2hl_150hn_fullRun/median_fitness_byGens.png")
```

@@

```{r, echo=FALSE, out.height="90%"}
knitr::include_graphics("~/masterThesis/master_thesis/img/PT_Strategies_airfoil_2hl_150hn_fullRun/median_Size_best_solution.png")
```

@@

```{r, echo=FALSE, out.height="90%"}
knitr::include_graphics("~/masterThesis/master_thesis/img/PT_Strategies_airfoil_2hl_150hn_fullRun/median_lev_div_overGens.png")
```

@@

```{r, echo=FALSE, out.height="90%"}
knitr::include_graphics("~/masterThesis/master_thesis/img/PT_Strategies_airfoil_2hl_150hn_fullRun/mean_epochs_trained_perGen.png")
```

>>>>

---
title: "Pre-Trained Denoising Autoencoders Long Short-Term Memory Networks as probabilistic
  Models for Estimation of Distribution Genetic Programming"
author: "Roman Hoehn"
date: 'Datum: 25.01.2023'
output:
  beamer_presentation:
    theme: Madrid
    fonttheme: structurebold
    fig_caption: no
    number_sections: yes
    slide_level: 2
subtitle: 'Kolloquium zur Masterarbeit im M.Sc. Wirtschaftspädagogik '
link-citations: yes
institute: JGU Mainz
toc: yes
bibliography: ref/ref.bib
csl: "csl/harvard-cite-them-right.csl"
lang: de
# includes:
#   in_header: header_files/slides.tex
---

@@

```{r echo=FALSE, out.height="90%", out.width="50%"}
knitr::include_graphics("./img/flowcharts/dae-gp.png")
```

@@

```{r, echo=FALSE, out.height="90%", out.width="50%"}
knitr::include_graphics("./img/flowcharts/pt-dae-gp.png")
```

@@

```{r, echo=FALSE, out.height="85%", out.width="80%"}
knitr::include_graphics("~/masterThesis/master_thesis/img/airfoil_2hl_maxIndSize_fullRun_30gens_withGP/median_fitness_byGens.png")
```

@@

```{r, echo=FALSE, out.height="85%", out.width="80%"}
knitr::include_graphics("~/masterThesis/master_thesis/img/airfoil_2hl_maxIndSize_fullRun_30gens/final_fit_boxplot.png")
```

@@

```{r, echo=FALSE, out.height="85%", out.width="80%"}
knitr::include_graphics("~/masterThesis/master_thesis/img/airfoil_2hl_maxIndSize_fullRun_30gens_withGP/median_best_Size_byGens.png")
```

@@

```{r, echo=FALSE, out.height="85%", out.width="80%"}
knitr::include_graphics("/Users/rmn/github/master_thesis/img/airfoil_2hl_maxIndSize_fullRun_30gens_withGP/median_popDiversity_byGens_levOnly_withGP.png")
```

@@

```{r, echo=FALSE, out.height="85%", out.width="80%"}
knitr::include_graphics("/Users/rmn/github/master_thesis/img/airfoil_2hl_maxIndSize_fullRun_30gens_TimeBenchmark/median_runtime.png")
```

@@

```{r, echo=FALSE, out.height="85%", out.width="80%"}
knitr::include_graphics("/Users/rmn/github/master_thesis/img/airfoil_2hl_maxIndSize_fullRun_30gens_TimeBenchmark/median_training_epochs.png")
```

@@

```{r, echo=FALSE, out.height="85%", out.width="80%"}
knitr::include_graphics("/Users/rmn/github/master_thesis/img/airfoil_2hl_maxIndSize_fullRun_30gens_TimeBenchmark/median_sampleTime.png")
```

@@

```{r, echo=FALSE, out.height="85%", out.width="80%"}
knitr::include_graphics("/Users/rmn/github/master_thesis/img/Airfoil_RuntimeProfiling/Runtime_Bar.png")
```

@@

```{r, echo=FALSE, out.height="85%", out.width="80%"}
knitr::include_graphics("~/masterThesis/master_thesis/img/airfoil_1hl_maxIndSize_fullRun_30gens/median_fitness_byGens.png")
```

@@

```{r, echo=FALSE, out.height="85%", out.width="80%"}
knitr::include_graphics("~/masterThesis/master_thesis/img/airfoil_1hl_maxIndSize_fullRun_30gens/final_fit_boxplot.png")
```

@@

```{r, echo=FALSE, out.height="85%", out.width="80%"}
knitr::include_graphics("~/masterThesis/master_thesis/img/airfoil_1hl_maxIndSize_fullRun_30gens/median_Size_byGens.png")
```

@@

```{r, echo=FALSE, out.height="85%", out.width="80%"}
knitr::include_graphics("~/masterThesis/master_thesis/img/symbolicRegressionSummarized/median_fitness_byGens.png")
```
<!-- ![Übersicht Median Fitness - Symbolische Regression](~/masterThesis/master_thesis/img/symbolicRegressionSummarized/median_fitness_byGens.png){height=80%} -->

@@

```{r full_run_realWorldSymReg_fitness, echo=FALSE, message=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
library(dplyr)

@@

```{r, echo=FALSE, out.height="85%", out.width="80%"}
knitr::include_graphics("~/masterThesis/master_thesis/img/symbolicRegressionSummarized/median_bestSol_size_byGens.png")
```

@@

```{r, echo=FALSE, out.height="85%", out.width="80%"}
knitr::include_graphics("~/masterThesis/master_thesis/img/symbolicRegressionSummarized/median_levDistance_byGen.png")
```

@@

```{r, echo=FALSE, out.height="85%", out.width="80%"}
knitr::include_graphics("~/masterThesis/master_thesis/img/symbolicRegressionSummarized/median_epochsTrained.png")
```

@@

```{r, echo=FALSE, out.height="85%", out.width="80%"}
knitr::include_graphics("~/masterThesis/master_thesis/img/PT_Strategies_airfoil_2hl_150hn_fullRun/median_fitness_byGens.png")
```

@@

```{r, echo=FALSE, out.height="85%", out.width="80%"}
knitr::include_graphics("~/masterThesis/master_thesis/img/PT_Strategies_airfoil_2hl_150hn_fullRun/median_Size_best_solution.png")
```

@@

```{r, echo=FALSE, out.height="85%", out.width="80%"}
knitr::include_graphics("~/masterThesis/master_thesis/img/PT_Strategies_airfoil_2hl_150hn_fullRun/median_lev_div_overGens.png")
```

@@

```{r, echo=FALSE, out.height="85%", out.width="80%"}
knitr::include_graphics("~/masterThesis/master_thesis/img/PT_Strategies_airfoil_2hl_150hn_fullRun/mean_epochs_trained_perGen.png")
```
